\section{Introduction}\label{sec:intro}

%^C In one paragraph: introduce Software Supply Chain.
%^C How vital is it? (accelerate development; provide usable components)
%^C How severely has it been compromised?
%^C List examples of SSC attacks (xz-utils, log4j)
\par The Software Supply Chain (SSC) lies at the basis of modern digital
infrastructure. By providing software developers with reusable libraries,
packages, or components which can be assembled into a larger software
project\citep{sscdirection}, Software Supply Chain is integral to boosting
development efficacy, improving software quality, and reduce development cost
\citep{brooks1987no,mythicalmanmonth}. However, the number of Software Supply
Chain attacks, which come in the form of ransomware, backdoor, or vulnerability
injected into the source code, has grown exponentially over recent years.
This can be evidenced by the surging number of Common Vulnerabilities and
Exposures (CVEs), indicating the wide susceptibility of softwares. Also
Sonatype, an software supply chain platform, observed an annual increase of 156\%
in number of malicious packages, reaching a startling number of 704,102 identified
since 2019 \citep{sonatype2024report}. Such proliferation of malicious or
vulnerable components,
coupled with exploding consumption of open-source packages and failure to
promptly respond to reported vulnerabilities such as CVEs 
\citep{sonatype2024report}, have profound
implications to the security and trustworthiness of Software Supply Chain,
since common consequences of Software Supply Chain
breach include financial or data loss, distrust in open-source ecosystem
, and ultimately higher software development cost.
For instance, the \texttt{xz-util} incident is an example of deliberately
injected backdoor, allowing the attacker to intercept sensitive data
or gain control of the affected machine \citep{xzincident}, and a trust
is undermined.
Despite all on-going efforts for security 
assurance and attack detection (e.g. \citep{konala25metadata,11022932,10695665}),
the sheer volume of risk to the
security of Software Supply Chain calls for new methods of governance.

%^C Introduce Large language model, in a more general way.
\par Recent advancements in Large Language Models (LLMs), including
improvement in model's intrinsic
capabilities\citep{llmsurvey,overviewllm,csllm} and the introduction of
enhancement techniques, contributed to their active involvement in
software engineering tasks, such as code suggestion, code completion, and
code review \citep{llm4se, llm4se2}. Because of their contextual reasoning
capabilities and understanding of code intent, several studies have
explored leveraging these language models for guarding the security
of Software Supply Chain, in the following ways:

\begin{itemize}
  \item \textit{Attack Detection} (e.g. 
  \citep{llmbackdoordet,singla2023empiricalstudyusinglarge,syed2025agenticaiautonomousdefense}).
  By studying source code patterns of ransomware and backdoor,
  Large Language Models can be leveraged as classifiers to
  help package distribution sites eliminate malicious software components.

  \item \textit{Vulnerability Detection} (e.g. \citep{11022932,10695665,10628694}).
  By analyzing threat models and
  searching for Common Weakness Enumerations (CWEs) in the source code, 
  vulnerabilities can be fixed before they persist to a released package.

  \item \textit{Vulnerability Repair} (e.g.
  \citep{vulrepairusingllm,vulmaster}). Large Language Models can be
  leveraged for automated vulnerability resolution, thereby accelerating
  the process of patching a known vulnerability before exploitation.
\end{itemize}

\par Nevertheless, Large Language Models may be used for both defending the
security of Software Supply Chain, and also attacking it. This study reviews and
hypothesizes several scenarios where LLM can assist attacking Software
Supply Chain, and provides their respective attack vector.

\par To the best of our knowledge, this study is the first to examine the
Large Language Model's implications of the security of Software Supply Chain.
It makes the following contributions:

\begin{itemize}
  \item A Systematic Literature Review on "LLM for Software Supply Chain",
  which identifies research advancements and gaps.

  \item A literature review of studies in which LLM is leveraged for attacking
  purposes. We also hypothesize other possible scenarios.

  \item Insights into mitigation of LLM-assisted Software Supply Chain
  attacks. They serve as guidance to responsible, ethical, and non-malignant
  use of LLM in Software Supply Chain.
\end{itemize}

